\section{Conclusion and Future Work}
\label{sec:Conclusion}
This project started off as an analytical task, but quickly transitioned to a optimization and research project, as the fine-tuning and optimization of topic modeling algorithms proved to be far more exciting with a lot of depth to explore. We broke away from the defaultness of black-box pre-processing algorithms by constructing tailored pipelines and optimizing legacy algorithms to their best capabilities, allowing them to generate topics up to par with the state-of-the-art. Algorithms such as LSI, LDA, HDP and ProdLDA were put on the spot against BERTopic, which offers a variety of conveniences and is justifiably sitting at the SOTA throne for topic models. The ambiguity of quantitatively evaluating unsupervised topic models was a constant concern that led to a lot of second-guessing and the human factor was crucial to finding the best model.

Our work sets the baseline for unsupervised topic modeling in Hellenistic corpora, with a key takeaway being that English-based approaches such as spaCy and multilingual sentence transformers are outperformed by niche, yet well tailored, toolkits and models. The analysis was not groundbreaking - it was no surprise to anyone that Greece went over an economic crisis or that COVID-19 was a very hot topic - but the frozen-in-time model approach offered a retrospective view that while not as interesting, is certainly accurate and can prove useful in real-world scenarios.

Due to limitations in both time and project length, only the iceberg of our findings was presented. As an additional contribution to the field, all of our analysis is available in the project's open-source repository \citep{Rigatos;Giannakopoulos:24}. Further experimentation with an alternative input data granularity (sentences, paragraphs) and a more generous topic allowance could result in deeper insights with regards to understated events. Finally, additional approaches such as zero-shot, multi-modal and dynamic (over time) topic modeling make for interesting tasks to be tackled, especially in Greek.